%-------------------------
% Resume in Latex
% Author : Devesh
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------

\begin{center}
    {\huge Devesh Rai} \\ \vspace{2pt} 
    {+91 8828403125} ~ 
    \small{-}
    \href{https://devesh-rai.vercel.app/}{\underline{\color{blue}{Portfolio}}} ~
    \small{-}
    \href{mailto:deveshrai162@gmail.com}{\underline{\color{blue}{deveshrai162@gmail.com}}} ~ 
    \small{-}
    \href{https://www.linkedin.com/in/devesh-rai-544437230/}{\underline{\color{blue}{Linkedin}}}  ~
    \small{-}
    \href{https://github.com/devesshhh}{\underline{\color{blue}{Github}}} ~
    
    \vspace{-7pt}
\end{center}



%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading
    {PACE Junior Science College, Thane}{Thane, India}
    {Higher Secondary (12th Grade) - Science\hspace{1em} \textbf{89\%}}{August 2021}
  \resumeSubheading
    {Thakur College of Engineering and Technology, Kandivali}{Mumbai, India}
    {Bachelor of Engineering in Computer Engineering\hspace{1em} \textbf{9.5 CGPA}}{December 2021 - June 2025}
\resumeSubHeadingListEnd
\vspace{-10pt}


%-----------WORK EXPERIENCE-----------
\section{\color{airforceblue}INTERNSHIPS}
\resumeSubHeadingListStart

  \resumeSubheading
    {Web Development Intern}{Thane, India} 
    {Dental-HiFi}{March 2024 - June 2024}
    \resumeItemListStart
      \resumeItem{\normalsize{Developed the frontend of the Dental-HiFi working website using REACT.js. Implemented responsive and user-friendly interfaces to enhance user experience. \href{https://drive.google.com/file/d/1eaM-8C_qFsmET548P7MkhQSXwVTHwZpW/view?usp=drive_link}{\color{blue}\underline{[Proof of Work]}}}}
    \resumeItemListEnd

  \resumeSubheading
    {Backend Developer Intern}{Mumbai, India} 
    {Shweta Associates and Garments}{December 2023 - February 2024}
    \resumeItemListStart
      \resumeItem{\normalsize{Collaborated with the development team to develop and maintain server-side logic, ensuring robust backend functionality. Optimized database performance and implemented RESTful APIs. \href{https://drive.google.com/file/d/1xRLp-hwEZDqDbhVVknuCzp9uUAr0891W/view?usp=drive_link}{\color{blue}\underline{[Proof of Work]}}}}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-12pt}



%-----------TECHNICAL SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, C\#, TypeScript}} \\
     \textbf{\normalsize{Tools and Technologies:}}{ \normalsize{Microsoft Fabric, Databricks, Power BI, Git, PySpark, T-SQL, Notebooks, Pipelines}} \\
     \textbf{\normalsize{Frameworks and Libraries:}}{ \normalsize{Angular 17, .NET Core, Entity Framework Core, Spark MLlib}} \\
     \textbf{\normalsize{Machine Learning:}}{ \normalsize{Imputation, Encoding, Feature Engineering, AutoML, Model Training, Hyperparameter Tuning, Evaluation, MLflow, MLOps, Unity Catalog}} \\
     \textbf{\normalsize{Databases:}}{ \normalsize{SQL Server, MongoDB}} \\
     \textbf{\normalsize{CS Fundamentals:}}{ \normalsize{Data Structures and Algorithms, Object-Oriented Programming, Computer Networks, Database Management Systems, Operating Systems, Software Development Life Cycle}} \\
     }}
 \end{itemize}
 \vspace{-12pt}


%-----------CLOUD & CERTIFICATIONS-----------
\section{\color{airforceblue}CLOUD \& CERTIFICATIONS}
\begin{itemize}[leftmargin=0in, label={}]
 \small{\item{
  \textbf{AWS Services:} S3, IAM, EC2, CloudWatch, VPC, ECS, Route 53 \\
  \textbf{AWS Tools:} AWS CLI, AWS CloudFormation, AWS CloudTrail \\
  \textbf{Certifications:}
    \begin{itemize}[leftmargin=1.5em, topsep=0.3em, itemsep=-0.2em, label={}]
      \item \textbf{Databricks Certified Machine Learning Associate} \href{https://credentials.databricks.com/fdcde26c-6207-4d93-80d2-6fe09ab94735\#acc.qMXAzn0T}{\color{blue}\faLink}
      \item \textbf{Microsoft Certified: Fabric Data Engineer Associate (DP-700)} \href{https://learn.microsoft.com/api/credentials/share/en-us/DeveshRai-1487/FF388F39A90590F?sharingId=1B3ED70FDCE861F0}{\color{blue}\faLink}
      \item \textit{AWS Certified Solutions Architect – Associate (In Progress)}
    \end{itemize}
  }}
\end{itemize}
\vspace{-12pt}





%-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}    
\resumeItemListStart

  \resumeItem{\normalsize{\textbf{Football Performance Analytics}, End-to-end analytics project using Microsoft Fabric and Databricks. Processed Kaggle datasets with PySpark, transformed data via Dataflow Gen2 and Notebooks, and built a 4-stage pipeline with Gmail notification. \href{https://github.com/devesshhh/ronaldo-performance-analytics-fabric-databricks}{\color{blue}\underline{[GitHub]}}}}

  \resumeItem{\normalsize{\textbf{Pharmacy Management System}, Full-stack Angular 17 + .NET Core app with SQL Server, JWT Auth, and role-based access (Admin, Doctor, Supplier). Features real-time inventory, order flow, cart, password reset via SMTP, and responsive UI. \href{https://github.com/devesshhh/pharmacy-app}{\color{blue}\underline{[GitHub]}}}}

  \resumeItem{\normalsize{\textbf{AWS Tasks and Videos}, A collection of AWS tasks and their demonstration videos. These tasks involve services such as EC2, S3, VPC, and more. \href{https://drive.google.com/drive/folders/18fmKjgLA8OFNMqCMs62jM4\_IFpDjkNi9?usp=sharing}{\color{blue}\underline{[Drive]}}}}

  \resumeItem{\normalsize{\textbf{Pet Cuddle O Tron}, A serverless AWS app to automate pet care tasks. Used Lambda, API Gateway, S3, SES, Step Functions, and DynamoDB for workflow orchestration, storage, and notifications. \href{https://drive.google.com/drive/folders/1gNZbKkDYxAuwtBbN5kctkvc1bQQYHC0V?usp=sharing}{\color{blue}\underline{[Drive]}}}}

\resumeItemListEnd

\vspace{-12pt}




%-----------ACHIEVEMENTS \& ACTIVITIES-----------
\section{\color{airforceblue}ACHIEVEMENTS \& ACTIVITIES}
\resumeItemListStart
    \resumeItem{\normalsize{Co-authored 3 research papers on quantum computing, data privacy in healthcare, and political ethics. Published in IJRPR, IJSRET, and IJNRD (2024). \href{https://ijrpr.com/uploads/V5ISSUE3/IJRPR24368.pdf}{\color{blue}\underline{[1]}} \href{https://ijsret.com/wp-content/uploads/2024/05/IJSRET_V10_issue3_109.pdf}{\color{blue}\underline{[2]}} \href{https://www.ijnrd.org/papers/IJNRD2405315.pdf}{\color{blue}\underline{[3]}}}}
    \resumeItem{\normalsize{Represented Thane district in Maharashtra State Sepaktakraw Championship (2018).}}
    \resumeItem{\normalsize{Runner-up – Grassroots Football Fiesta (2017).}}
    \resumeItem{\normalsize{Won school-level chess tournaments consistently (Grades 5–10).}}
\resumeItemListEnd
\vspace{-10pt}


\end{document}
